---
title: "p8105_hw6_ltc2121"
author: Lindsey Covell
output: github_document
---

```{r, include = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(p8105.datasets)
library(modelr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

To obtain a distribution for $\hat{r}^2$, we'll follow basically the same procedure we used for regression coefficients: draw bootstrap samples; the a model to each; extract the value I'm concerned with; and summarize. Here, we'll use `modelr::bootstrap` to draw the samples and `broom::glance` to produce `r.squared` values. 

```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.

We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

As with $r^2$, this distribution is somewhat skewed and has some outliers. 

The point of this is not to say you should always use the bootstrap -- it's possible to establish "large sample" distributions for strange parameters / values / summaries in a lot of cases, and those are great to have. But it is helpful to know that there's a way to do inference even in tough cases. 

## Problem 2 

#### Data import and manipulation 
```{r}
washp_df = 
  read_csv("data/homicide-data copy.csv") %>% 
  filter(victim_race %in% c("White", "Black")) %>% 
  mutate(city_state = str_c(city, state, sep = ", "),
         resolved = as.numeric(disposition == "Closed by arrest"),
          victim_age = as.numeric(victim_age),
          victim_race = fct_relevel(victim_race, "White"))  %>% 
  filter(city != "Dallas" & city != "Phoenix" & 
           city != "Kansas City" & city_state != "Tulsa, AL") 
```

#### Baltimore, MD glm

```{r}
balti_log = 
  washp_df %>% 
  filter(city == "Baltimore") %>%
  glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate), 
         CI_low = exp(estimate - 1.96 * std.error), 
         CI_high = exp(estimate + 1.96 * std.error)) %>%
  filter(term == "victim_sexMale") %>% 
  select(term, OR, CI_low, CI_high) %>% 
  knitr::kable(digits = 3)
```

The results of the logistic regression in the table show that keeping all other variables fixed, homicides in which the victim is male are significantly less like to be resolved than those in which the victim is female.

#### All cities glm

```{r}
wash_logit = 
  washp_df %>% 
  select(city_state, resolved, victim_age, victim_race, victim_sex) %>% 
  nest(data = resolved:victim_sex) %>% 
  mutate(
    city_logs = map(.x = data, ~glm(resolved ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
  city_res = map(city_logs, broom::tidy)) %>% 
  unnest(city_res) %>% 
  mutate(OR = exp(estimate), 
         CI_low = exp(estimate - 1.96 * std.error), 
         CI_high = exp(estimate + 1.96 * std.error)) %>%
  filter(term == "victim_sexMale") %>% 
  select(city_state, term, OR, CI_low, CI_high) 

wash_logit %>% 
  knitr::kable(digits = 3)
  
```

#### Box plot for city estimates 

```{r}
wash_logit %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
ggplot() +
  geom_point(aes(x = city_state, y = OR)) +
  geom_errorbar( aes(x = city_state, ymin = OR - CI_low, ymax = OR + CI_high)) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 6)) +
   labs(
    title = "Odds of Homicide Being Solved", 
    subtitle = "Male Victims Compared to Female Victims",
    x = "US City",
    y = "Odds Ratio")
```

